Automated verification of electrical systems: literature review and case studies of stand-alone solar photovoltaics\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2019-01-21 Tex/CAV2019/Trindade_Cordeiro_CAV2019.tex
reviewed introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}. Progress has been made worldwide; in particular, the number of people without electricity access fell below 1 billion for the first time in 2017~\cite{IEAweo2018}. In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the least-cost solution for three-quarters of the additional connections needed; \textcolor{red}{This sentence is unclear... what is the ``role to play''?} however, that grid extension will still have a role to play, especially in urban areas~\cite{IEAweo2018}.

@@

Formal methods based on \textit{model checking} can offer a great potential to obtain a more effective and faster verification in the design process of PV systems~\cite{ClarkeHV18}. In this study, we review verification tools for PV systems and also present five case studies, where different model checking tools are compared in terms of performance and reliability when validating stand-alone solar PV systems.

In order to compare different model checkers, we developed a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter and electrical load. Design requirements as battery autonomy and power demand in addition to weather conditions, as solar irradiance and ambient temperature, are translated as part of that model and automatically checked by the employed verifiers, which report under which conditions a system does not meet the user requirements.

The main contribution of this approach is that it aids to detect design flaws in PV systems, thus considerably improving system reliability~\cite{Akram2018}; our case studies are empirical and they were deployed in 2018 with feedback information collected from monitoring systems via micro-controllers and by means of interviews with dwellers.

>>>>

Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}. Progress has been made worldwide; in particular, the number of people without electricity access fell below 1 billion threshold for the first time in 2017~\cite{IEAweo2018}. In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed; \textcolor{red}{This sentence is unclear... what is the ``role to play''?} however, that grid extension will still have a role to play, especially in urban areas~\cite{IEAweo2018}.

@@

Formal methods based on \textit{model checking} can offer a great potential to obtain a more effective design process of PV systems~\cite{ClarkeHV18}. In this study, we review verification tools for PV systems and also present five case studies, where different model checking tools are compared in terms of performance and reliability when validating stand-alone solar PV systems. In order to compare different model checkers, we developed a mathematical model of each component of a stand-alone PV system, including solar panel, charge controller, batteries, inverter and electrical load. Design requirements as battery autonomy and power demand in addition to weather conditions, as solar irradiance and ambient temperature, are translated as part of that model and automatically checked by the employed model checkers.

The main contribution of this approach is that it automatically aids to detect design flaws in PV systems by reporting under which conditions a system does not meet the user requirements, thus considerably improving system's reliability~\cite{Akram2018}. Our case studies are empirical; they were deployed in 2018 with feedback information collected from monitoring systems via micro-controllers and by means of interviews with dwellers with the goal of validating our results.
